Source Summaries

### 2020-03-02 paper/sourceSummaries/summary5.tex

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{BLE Injection-Free Attack: A Novel Attack On Bluetooth Low Energy Devices}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{jaihc19}

@@

\noindent
The authors propose a new method of attacking the cryptography of BLE devices, called an injection-free attack. The authors propose this attack for when forced key renegotiation is not possible.

@@

\noindent
The theory being used is Game Theory. The authors are attacking BLE devices in a zero sum game.

@@

\noindent
The authors use a BLE device with enough interfaces to fill the bonding list of a target device. An attacker will keep pairing new devices to the target until the bonding list fills up. Once this occurs, the next device to join will cause the target device to forget a key and negotiate a new one with the new device. Now the target device will need to renegotiate keys with legitimate devices. The attacker could carry out this attack without the packet injection needed in other attacks.

@@

\noindent
The authors found that it is remarkably easy to attack BLE devices even without abuse the weak cryptography due to the limited resources of the devices. This method could be used by attackers to maliciously pair with devices and remove legitimate devices from the bonding list of devices.

@@

\noindent
The authors believe that future research should go into automating injection free attacks and the development of defenses against such attacks.
